### 2019-02-11 museum.tex
changes and comments
final version

>>>>

\cite[Chapter 6,7]{Kop2012}).
\CK{If space happens to permit, we can replace the pointer to my thesis by
cite\{kop:raa:12,suz:kus:bla:11\}, but this does require 4 extra lines
of references.}

From the definition we immediately see that all encodings have the expected types:

\begin{lemma}\label{lem:encodings_types}
  \begin{enumerate}
  \item If $\Gamma \proves t_1 : \sigma$ and $\Gamma \proves t_2 :
    \tau$ then $\Gamma \proves \pair{t_1}{t_2} : \sigma \times \tau$.
  \item If $\Gamma \proves t : \tau_1 \times \tau_2$ then $\Gamma
    \proves \pi^i(t) : \tau_i$.
  \item If $\Gamma \proves t : \sigma[\subst{\alpha}{\tau}]$ then
    $\Gamma \proves \expair{\tau}{t} : \Sigma \alpha . \sigma$.
  \item If $\Gamma \proves t : \Sigma \alpha . \sigma$ and
    $\Gamma,x:\sigma \proves s : \rho$ and $\alpha \notin
    \FTV(\Gamma,\rho)$ then $\xlet{}{t}{\alpha,x}{s} : \rho$.
  \end{enumerate}
\end{lemma}

In addition, $\beta$-reduction provides the desired reduction rules:

\begin{lemma}\label{lem:encodings_reduce}
  $\pi^i(\pair{t_1}{t_2}) \leadsto_\beta^* t_i$ and
  $\xlet{}{\expair{\tau}{t}}{\alpha,x}{s} \leadsto_\beta^*
  s[\subst{\alpha}{\tau}][\subst{x}{t}]$.
\end{lemma}
